### 2017-03-14 thesis/misc/appendix.tex
Draft thesis completed; now edit the whole thing - tmp commit

	\chapter{Additional results for \cref{cha:obesity_genetic_signatures_and_cancer}}
	\label{app:a}

@@

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.45\linewidth,page=1]{appendix/check_raw_vs_std_mg}
		\hfill
		\includegraphics[width=0.45\linewidth,page=2]{appendix/check_raw_vs_std_mg}
		\caption{Scatter plots showing the raw and ranked Creighton \textit{et al.} obesity metagene values generated from standardised or non-standardised CR data set. }
		\label{fig:appendix/check_raw_vs_std}
	\end{figure}

@@

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.45\linewidth,page=1]{appendix/crtcga_raw_vs_std}
		\hfill
		\includegraphics[width=0.45\linewidth,page=2]{appendix/crtcga_raw_vs_std}\\
		\caption{Scatter plots comparing the Creighton \textit{et al.} obesity metagene generated from transformation matrix (from standardised or non-standardised CR data) in non-standardised (left) and standardised (right) \gls{icgc} \gls{blca} data.}
		\label{fig:appendix/check_raw_vs_std}
	\end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.45\linewidth,page=3]{appendix/crtcga_raw_vs_std}
		\hfill
		\includegraphics[width=0.45\linewidth,page=4]{appendix/crtcga_raw_vs_std}\\
		\caption{Scatter plots comparing the Creighton \textit{et al.} obesity metagene generated from transformation matrix from non-standardisedright (left) or standardised (right) CR data in non-standardised  and standardised  \gls{icgc} \gls{blca} data.}
		\label{fig:appendix/check_raw_vs_std_tm}
	\end{figure}

	\section{Remainder of the results of Creighton \textit{et al.} obesity metagenes in the \gls{icgc} cancer data sets}
	\label{sec:rest_of_the_cr_icgc_cancer_heatmap_results}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=8]{appendix/crtcga_std}\\
		\vspace{1em}
		\includegraphics[width=0.32\linewidth,page=13]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=23]{appendix/crtcga_std}\\
		\vspace{1em}
		\includegraphics[width=0.32\linewidth,page=28]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=38]{appendix/crtcga_std}\\
		\caption{Heatmaps showing the association of obesity metagene from the \citet{Creighton2012} study with sample gene expression from the other \gls{icgc} data sets.
	Level of expression is represented in the top right histogram, where low and high gene expression were colour-coded with blue and red, respectively.
	Each row of the heatmap represents a gene from the obesity associated genetic signature, and each column of the heatmap represents a sample from the \gls{icgc} data.
	The obesity associated metagene scores of the samples are shown in a separate row at top of the heatmap, and the tree diagram of the heirarchical clustering of the genes is shown to the left of the heatmap. }
		\label{fig:appendix/cr_icgc_heatmap}
	\end{figure}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=9,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/crtcga_std}\\
		\includegraphics[page=14,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/crtcga_std}\\
		\caption{Box plots and scatter plots showing the association of obesity metagene from the \citet{Creighton2012} study with the sample \gls{bmi} status  and \gls{bmi} from the other \gls{icgc} data sets, respectively.
	In the box plot, the p-values above the groups represent the statistical significance of the association of the metagene with the overweight or obese group compared with the normal weight group.
	The \gls{anova} p-value shows the statistical significance of the association of the metagene with the sample \gls{bmi} groups.
	In the scatter plot, $R^2$- and p-values describe the adjusted coefficient of determination of the regression line and the statistical significance of the linear model used to draw the regression line, respectively.}
		\label{fig:appendix/cr_icgc_box_scatter}
	\end{figure}

@@

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{cesc} cancer data}
	\label{tab:degmetacesc}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.9332                      & 0.5302  & 0.7622             & -0.003950  & 0.7265              \\
            Res     & 0.9205                      & 0.3369  & 0.6043             & 0.004249   & 0.8122              \\
            CrOl    & 0.8940                      & 0.1430  & 0.2959             & -0.0004927 & 0.3465              \\
            ResOl   & 0.9930                      & 0.1705  & 0.3078             & 0.003263   & 0.1898              \\
            Ca      & 0.8861                      & 0.3616  & 0.6426             & -0.003307  & 0.6073              \\
            CaRes   & 0.8323                      & 0.3330  & 0.6167             & -0.003832  & 0.7001              \\
            CaOl    & 0.9124                      & 0.1602  & 0.2600             & -0.001612  & 0.4242              \\
            CaResOl & 0.9646                      & 0.1663  & 0.2863             & 0.003097   & 0.1946              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{coad} cancer data}
	\label{tab:degmetacoad}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.2843                      & 0.8176  & 0.5460             & -0.004373  & 0.8865              \\
            Res     & 0.4091                      & 0.8473  & 0.7064             & -0.004243  & 0.8245              \\
            CrOl    & 0.4063                      & 0.9295  & 0.6150             & -0.00397   & 0.7400              \\
            ResOl   & 0.3748                      & 0.8484  & 0.5295             & -0.004020  & 0.7532              \\
            Ca      & 0.6507                      & 0.7692  & 0.7579             & -0.002493  & 0.5075              \\
            CaRes   & 0.4565                      & 0.9808  & 0.7161             & -0.004278  & 0.8385              \\
            CaOl    & 0.2931                      & 0.9217  & 0.4621             & -0.00425   & 0.8273              \\
            CaResOl & 0.4203                      & 0.9087  & 0.7017             & -0.004461  & 0.9800              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{kirp} cancer data}
	\label{tab:degmetakirp}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.1853                      & 0.2590  & 0.3387             & -0.005657  & 0.5798              \\
            Res     & 0.1063                      & 0.1825  & 0.2128             & -0.005037  & 0.5368              \\
            CrOl    & 0.2576                      & 0.1757  & 0.3162             & -0.005763  & 0.5879              \\
            ResOl   & 0.3120                      & 0.1738  & 0.3198             & -0.004513  & 0.5048              \\
            Ca      & 0.2431                      & 0.2142  & 0.3591             & -0.005582  & 0.5743              \\
            CaRes   & 0.2327                      & 0.2344  & 0.3738             & -0.006250  & 0.6279              \\
            CaOl    & 0.3426                      & 0.2775  & 0.4693             & -0.007333  & 0.77469             \\
            CaResOl & 0.2643                      & 0.1315  & 0.2410             & -0.001408  & 0.3649              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{lihc} cancer data}
	\label{tab:degmetalihc}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.4033                      & 0.2900  & 0.5221             & 0.006348   & 0.1028              \\
            Res     & 0.5008                      & 0.8743  & 0.8004             & -0.0003709 & 0.3430              \\
            CrOl    & 0.7599                      & 0.8562  & 0.9189             & -0.001554  & 0.4424              \\
            ResOl   & 0.9238                      & 0.9773  & 0.9938             & -0.001283  & 0.4162              \\
            Ca      & 0.4898                      & 0.8221  & 0.7917             & 0.0005899  & 0.2834              \\
            CaRes   & 0.5976                      & 0.9929  & 0.8638             & -0.001090  & 0.3990              \\
            CaOl    & 0.8717                      & 0.8834  & 0.9679             & -0.002010  & 0.4925              \\
            CaResOl & 0.5369                      & 0.7185  & 0.7073             & -0.0004212 & 0.3465              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{read} cancer data}
	\label{tab:degmetaread}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.9129                      & 0.4008  & 0.5942             & -0.0132    & 0.8038              \\
            Res     & 0.7737                      & 0.2244  & 0.4308             & -0.008917  & 0.5484              \\
            CrOl    & 0.8439                      & 0.1283  & 0.2643             & 0.001024   & 0.3036              \\
            ResOl   & 0.6953                      & 0.06841 & 0.1766             & 0.01099    & 0.1840              \\
            Ca      & 0.6298                      & 0.1326  & 0.2960             & -0.001242  & 0.3432              \\
            CaRes   & 0.6302                      & 0.1053  & 0.2453             & 0.001989   & 0.2885              \\
            CaOl    & 0.6871                      & 0.1411  & 0.3358             & -0.004847  & 0.4219              \\
            CaResOl & 0.8821                      & 0.08474 & 0.1817             & 0.001095   & 0.3025              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{skcm} cancer data}
	\label{tab:degmetaskcm}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.7115                      & 0.3329  & 0.6264             & 0.002887   & 0.2033              \\
            Res     & 0.7604                      & 0.5408  & 0.6396             & -0.001725  & 0.4296              \\
            CrOl    & 0.4719                      & 0.1224  & 0.2913             & 0.01261    & 0.05347             \\
            ResOl   & 0.8640                      & 0.1668  & 0.3051             & 0.01541    & {\bfseries 0.0372}\tnote{1}  \\
            Ca      & 0.8792                      & 0.2084  & 0.3739             & 0.006674   & 0.1184              \\
            CaRes   & 0.8098                      & 0.1950  & 0.3677             & 0.005746   & 0.1347              \\
            CaOl    & 0.9478                      & 0.2726  & 0.4471             & 0.01009    & 0.07449             \\
            CaResOl & 0.7309                      & 0.2561  & 0.2830             & 0.01606    & {\bfseries 0.03421} \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{ucec} cancer data}
	\label{tab:degmetaucec}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.8357                      & 0.08117 & 0.1039             & 0.006952   & {\bfseries 0.03716}\tnote{1}\\
            Res     & 0.8664                      & 0.2023  & 0.3131             & 0.001998   & 0.1619              \\
            CrOl    & 0.9251                      & 0.3800  & 0.5800             & -0.000311  & 0.3569              \\
            ResOl   & 0.5826                      & 0.09608 & 0.2156             & 0.003487   & 0.1021              \\
            Ca      & 0.7491                      & 0.1103  & 0.1905             & 0.003811   & 0.09260             \\
            CaRes   & 0.8086                      & 0.2002  & 0.3419             & 0.0005824  & 0.2584              \\
            CaOl    & 0.9068                      & 0.2672  & 0.4153             & 0.00305    & 0.1166              \\
            CaResOl & 0.8360                      & 0.2440  & 0.4034             & 0.00022898 & 0.2863              \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=8]{appendix/cris_crdeg_trans_meta}\\
		\includegraphics[width=0.32\linewidth,page=13]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=23]{appendix/cris_crdeg_trans_meta}\\
		\includegraphics[width=0.32\linewidth,page=28]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=38]{appendix/cris_crdeg_trans_meta}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the \gls{nzbc} data set.
	Scales are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_heatmap_cris}
	\end{figure}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=9,width=0.42\linewidth]{appendix/cris_crdeg_trans_meta}
		\hfill
		\includegraphics[page=10,width=0.42\linewidth]{appendix/cris_crdeg_trans_meta}\\
		\caption{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{nzbc} data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_cris}
	\end{figure}

>>>>

	\chapter{Additional results from \cref{cha:obesity_genetic_signatures_and_cancer}}
	\label{app:a}

@@

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.45\linewidth,page=1]{appendix/check_raw_vs_std_mg}
		\hfill
		\includegraphics[width=0.45\linewidth,page=2]{appendix/check_raw_vs_std_mg}
		\caption[Comparison of the raw and ranked Creighton \textit{et al.} obesity metagene scores from the standardised or non-standardised CR data]{Scatter plots showing the raw and ranked Creighton \textit{et al.} obesity metagene scores from the standardised or non-standardised CR data.
		The \gls{rma}-normalised CR data was standardised or used as is to generate the obesity metagene scores.
		The metagene scores were ranked based on the number of samples in the CR data set.
		}
		\label{fig:appendix/check_raw_vs_std}
	\end{figure}

@@

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.45\linewidth,page=1]{appendix/crtcga_raw_vs_std}
		\hfill
		\includegraphics[width=0.45\linewidth,page=2]{appendix/crtcga_raw_vs_std}\\
		\caption[Comparison of the Creighton \textit{et al.} obesity metagene generated from the standardised or non-standardised TM]{Scatter plots comparing the Creighton \textit{et al.} obesity metagene generated from the transformation matrix (from standardised or non-standardised CR data) in the non-standardised (left) and standardised (right) \gls{icgc} \gls{blca} data.}
		\label{fig:appendix/check_raw_vs_std}
	\end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.45\linewidth,page=3]{appendix/crtcga_raw_vs_std}
		\hfill
		\includegraphics[width=0.45\linewidth,page=4]{appendix/crtcga_raw_vs_std}\\
		\caption[Comparison of the Creighton \textit{et al.} obesity metagene generated from the standardised or non-standardised  \gls{icgc} \gls{blca} data]{Scatter plots comparing the Creighton \textit{et al.} obesity metagene from the non-standardised  and standardised  \gls{icgc} \gls{blca} data, generated by the application of the transformation matrix from the non-standardised (left) or standardised (right) CR data.}
		\label{fig:appendix/check_raw_vs_std_tm}
	\end{figure}

	\section{Remainder of the results of the other Creighton \textit{et al.} obesity metagenes in the \gls{icgc} cancer data sets}
	\label{sec:rest_of_the_cr_icgc_cancer_heatmap_results}

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=8]{appendix/crtcga_std}\\
		\vspace{1em}
		\includegraphics[width=0.32\linewidth,page=13]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=23]{appendix/crtcga_std}\\
		\vspace{1em}
		\includegraphics[width=0.32\linewidth,page=28]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=38]{appendix/crtcga_std}\\
		\caption[Obesity metagene from the \citet{Creighton2012} study and the sample gene expressions in the other \gls{icgc} cancer types]{Heatmaps showing the association of obesity metagene from the \citet{Creighton2012} study with sample gene expression from the other \gls{icgc} data sets.
	Level of expression is represented in the top right histogram, where low and high gene expression were colour-coded with blue and red, respectively.
	Each row of the heatmap represents a gene from the obesity associated genetic signature, and each column of the heatmap represents a sample from the \gls{icgc} data.
	The obesity associated metagene scores of the samples are shown in a separate row at top of the heatmap, and the tree diagram of the heirarchical clustering of the genes is shown to the left of the heatmap. }
		\label{fig:appendix/cr_icgc_heatmap}
	\end{figure}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=9,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/crtcga_std}\\
		\includegraphics[page=14,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/crtcga_std}\\
		\caption[Obesity metagene from the \citet{Creighton2012} study and the sample \gls{bmi}/\gls{bmi} status in the other \gls{icgc} cancer types]{Box plots and scatter plots showing the association of obesity metagene from the \citet{Creighton2012} study with the sample \gls{bmi} status  and \gls{bmi} from the other \gls{icgc} data sets, respectively.
	In the box plot, the p-values above the groups represent the statistical significance of the association of the metagene with the overweight or obese group compared with the normal weight group.
	The \gls{anova} p-value shows the statistical significance of the association of the metagene with the sample \gls{bmi} groups.
	In the scatter plot, $R^2$- and p-values describe the adjusted coefficient of determination of the regression line and the statistical significance of the linear model used to draw the regression line, respectively.}
		\label{fig:appendix/cr_icgc_box_scatter}
	\end{figure}

@@

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{cesc} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{cesc} cancer data}
	\label{tab:degmetacesc}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.9332                      & 0.5302  & 0.7622             & -0.003950  & 0.7265              \\
            Res     & 0.9205                      & 0.3369  & 0.6043             & 0.004249   & 0.8122              \\
            CrOl    & 0.8940                      & 0.1430  & 0.2959             & -0.0004927 & 0.3465              \\
            ResOl   & 0.9930                      & 0.1705  & 0.3078             & 0.003263   & 0.1898              \\
            Ca      & 0.8861                      & 0.3616  & 0.6426             & -0.003307  & 0.6073              \\
            CaRes   & 0.8323                      & 0.3330  & 0.6167             & -0.003832  & 0.7001              \\
            CaOl    & 0.9124                      & 0.1602  & 0.2600             & -0.001612  & 0.4242              \\
            CaResOl & 0.9646                      & 0.1663  & 0.2863             & 0.003097   & 0.1946              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{coad} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{coad} cancer data}
	\label{tab:degmetacoad}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.2843                      & 0.8176  & 0.5460             & -0.004373  & 0.8865              \\
            Res     & 0.4091                      & 0.8473  & 0.7064             & -0.004243  & 0.8245              \\
            CrOl    & 0.4063                      & 0.9295  & 0.6150             & -0.00397   & 0.7400              \\
            ResOl   & 0.3748                      & 0.8484  & 0.5295             & -0.004020  & 0.7532              \\
            Ca      & 0.6507                      & 0.7692  & 0.7579             & -0.002493  & 0.5075              \\
            CaRes   & 0.4565                      & 0.9808  & 0.7161             & -0.004278  & 0.8385              \\
            CaOl    & 0.2931                      & 0.9217  & 0.4621             & -0.00425   & 0.8273              \\
            CaResOl & 0.4203                      & 0.9087  & 0.7017             & -0.004461  & 0.9800              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{kirp} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{kirp} cancer data}
	\label{tab:degmetakirp}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.1853                      & 0.2590  & 0.3387             & -0.005657  & 0.5798              \\
            Res     & 0.1063                      & 0.1825  & 0.2128             & -0.005037  & 0.5368              \\
            CrOl    & 0.2576                      & 0.1757  & 0.3162             & -0.005763  & 0.5879              \\
            ResOl   & 0.3120                      & 0.1738  & 0.3198             & -0.004513  & 0.5048              \\
            Ca      & 0.2431                      & 0.2142  & 0.3591             & -0.005582  & 0.5743              \\
            CaRes   & 0.2327                      & 0.2344  & 0.3738             & -0.006250  & 0.6279              \\
            CaOl    & 0.3426                      & 0.2775  & 0.4693             & -0.007333  & 0.77469             \\
            CaResOl & 0.2643                      & 0.1315  & 0.2410             & -0.001408  & 0.3649              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{lihc} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{lihc} cancer data}
	\label{tab:degmetalihc}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.4033                      & 0.2900  & 0.5221             & 0.006348   & 0.1028              \\
            Res     & 0.5008                      & 0.8743  & 0.8004             & -0.0003709 & 0.3430              \\
            CrOl    & 0.7599                      & 0.8562  & 0.9189             & -0.001554  & 0.4424              \\
            ResOl   & 0.9238                      & 0.9773  & 0.9938             & -0.001283  & 0.4162              \\
            Ca      & 0.4898                      & 0.8221  & 0.7917             & 0.0005899  & 0.2834              \\
            CaRes   & 0.5976                      & 0.9929  & 0.8638             & -0.001090  & 0.3990              \\
            CaOl    & 0.8717                      & 0.8834  & 0.9679             & -0.002010  & 0.4925              \\
            CaResOl & 0.5369                      & 0.7185  & 0.7073             & -0.0004212 & 0.3465              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{read} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{read} cancer data}
	\label{tab:degmetaread}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.9129                      & 0.4008  & 0.5942             & -0.0132    & 0.8038              \\
            Res     & 0.7737                      & 0.2244  & 0.4308             & -0.008917  & 0.5484              \\
            CrOl    & 0.8439                      & 0.1283  & 0.2643             & 0.001024   & 0.3036              \\
            ResOl   & 0.6953                      & 0.06841 & 0.1766             & 0.01099    & 0.1840              \\
            Ca      & 0.6298                      & 0.1326  & 0.2960             & -0.001242  & 0.3432              \\
            CaRes   & 0.6302                      & 0.1053  & 0.2453             & 0.001989   & 0.2885              \\
            CaOl    & 0.6871                      & 0.1411  & 0.3358             & -0.004847  & 0.4219              \\
            CaResOl & 0.8821                      & 0.08474 & 0.1817             & 0.001095   & 0.3025              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{skcm} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{skcm} cancer data}
	\label{tab:degmetaskcm}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.7115                      & 0.3329  & 0.6264             & 0.002887   & 0.2033              \\
            Res     & 0.7604                      & 0.5408  & 0.6396             & -0.001725  & 0.4296              \\
            CrOl    & 0.4719                      & 0.1224  & 0.2913             & 0.01261    & 0.05347             \\
            ResOl   & 0.8640                      & 0.1668  & 0.3051             & 0.01541    & {\bfseries 0.0372}\tnote{1}  \\
            Ca      & 0.8792                      & 0.2084  & 0.3739             & 0.006674   & 0.1184              \\
            CaRes   & 0.8098                      & 0.1950  & 0.3677             & 0.005746   & 0.1347              \\
            CaOl    & 0.9478                      & 0.2726  & 0.4471             & 0.01009    & 0.07449             \\
            CaResOl & 0.7309                      & 0.2561  & 0.2830             & 0.01606    & {\bfseries 0.03421} \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{ucec} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{ucec} cancer data}
	\label{tab:degmetaucec}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.8357                      & 0.08117 & 0.1039             & 0.006952   & {\bfseries 0.03716}\tnote{1}\\
            Res     & 0.8664                      & 0.2023  & 0.3131             & 0.001998   & 0.1619              \\
            CrOl    & 0.9251                      & 0.3800  & 0.5800             & -0.000311  & 0.3569              \\
            ResOl   & 0.5826                      & 0.09608 & 0.2156             & 0.003487   & 0.1021              \\
            Ca      & 0.7491                      & 0.1103  & 0.1905             & 0.003811   & 0.09260             \\
            CaRes   & 0.8086                      & 0.2002  & 0.3419             & 0.0005824  & 0.2584              \\
            CaOl    & 0.9068                      & 0.2672  & 0.4153             & 0.00305    & 0.1166              \\
            CaResOl & 0.8360                      & 0.2440  & 0.4034             & 0.00022898 & 0.2863              \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

	\section{Remainder of the results of FM obesity metagenes in the \gls{icgc} cancer data sets}
	\label{sec:rest_of_the_fm_icgc_cancer_heatmap_results}

%TODO: add FM metagene plots for ICGC

@@

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=8]{appendix/cris_crdeg_trans_meta}\\
		\includegraphics[width=0.32\linewidth,page=13]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=23]{appendix/cris_crdeg_trans_meta}\\
		\includegraphics[width=0.32\linewidth,page=28]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=38]{appendix/cris_crdeg_trans_meta}\\
		\caption[Association of the other CR obesity metagenes with the sample gene expressions in the \gls{nzbc} data]{Heatmaps showing the association of the other obesity metagenes identified from the CR data with the sample gene expressions from the \gls{nzbc} data set.
	Scales are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_heatmap_cris}
	\end{figure}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=9,width=0.42\linewidth]{appendix/cris_crdeg_trans_meta}
		\hfill
		\includegraphics[page=10,width=0.42\linewidth]{appendix/cris_crdeg_trans_meta}\\
		\caption[Association of the other CR obesity metagenes with the sample \gls{bmi}/\gls{bmi} status in the \gls{nzbc} data]{Box plots and scatter plots showing the association of the other CR obesity metagenes with the sample \gls{bmi} status  and \gls{bmi} from the \gls{nzbc} data set, respectively.
	P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_box_scatter_cris}
	\end{figure}
